This is an example of article title

### 2019-08-29 paper.tex
start application section
alan

@@

\begin{figure}[h]
\centering \includegraphics[width=5in]{image8.png} \caption{Performance comparison for loading 815MB from the NYC taxi dataset}
\label{fig:nyctaxiload} 
\end{figure}
Our test for loading data is an 815 MB CSV file from the NYC Taxi
\& Limousine Commission’s records on every yellow cab trip in January
of 2017. Figure~\ref{fig:nyctaxiload} compares loading times of
this data where the date-time fields are parsed as time objects or
simply as strings.

@@

\begin{figure}[h]
\centering \includegraphics[width=5in]{image4.png} \caption{Query times for 3 different query types across various systems}
\label{fig:nyctaxiquery} 
\end{figure}

>>>>

\lstset{literate=
{─}{{\ucc{$--$}}}{1}
{±}{{\ucc{$\pm$}}}{1}
}

@@

\begin{figure*}[h]
\centering \includegraphics[width=5in]{image8.png} \caption{Performance comparison for loading 815MB from the NYC taxi dataset}
\label{fig:nyctaxiload} 
\end{figure*}
Our test for loading data is an 815 MB CSV file from the NYC Taxi
\& Limousine Commission’s records on every yellow cab trip in January
of 2017. Figure~\ref{fig:nyctaxiload} compares loading times of
this data where the date-time fields are parsed as time objects or
simply as strings.

@@

\begin{figure*}[h]
\centering \includegraphics[width=5in]{image4.png} \caption{Query times for 3 different query types across various systems}
\label{fig:nyctaxiquery} 
\end{figure*}

\section{Applications}

We breifly mention some applications of JuliaDB in the real-world. Julia Computing is using JuliaDB as a time-series database~\cite{wilmott2018} for large datasets.
